Revisiting the Relationship between Short-Chain Fatty Acids, the Microbiota, and Colorectal Tumors

### 2018-08-08 submission/manuscript.Rmd
change to normal referencing

**Figure 1. No change in SCFA measurements was observed between normal, adenoma, and carcinoma individuals using HPLC.** Acetate (A), butyrate (B), and propionate (C) concentrations in fecal samples of individuals without colon tumors (Control), adenomas, and carcinomas (C). The black lines indicate the median SCFA concentration. Acetate (D), butyrate (E), and propionate (F) concentrations in fecal samples before and after treatment for adenoma (yellow) and carcinoma (red). The black dots and lines represent the median change in SCFA concentration.

>>>>

**Figure 1. No change in SCFA measurements was observed between normal, adenoma, and carcinoma individuals using HPLC.** Acetate (A), butyrate (B), and propionate (C) concentrations in fecal samples of individuals without colon tumors (Normal), adenomas, and carcinomas (C). The black lines indicate the median SCFA concentration. Acetate (D), butyrate (E), and propionate (F) concentrations in fecal samples before and after treatment for adenoma (yellow) and carcinoma (red). The black dots and lines represent the median change in SCFA concentration.

### 2018-08-08 submission/manuscript.tex
change to normal referencing

\textbf{Figure 1. No change in SCFA measurements was observed between
normal, adenoma, and carcinoma individuals using HPLC.} Acetate (A),
butyrate (B), and propionate (C) concentrations in fecal samples of
individuals without colon tumors (Control), adenomas, and carcinomas
(C). The black lines indicate the median SCFA concentration. Acetate
(D), butyrate (E), and propionate (F) concentrations in fecal samples
before and after treatment for adenoma (yellow) and carcinoma (red). The
black dots and lines represent the median change in SCFA concentration.

>>>>

\textbf{Figure 1. No change in SCFA measurements was observed between
normal, adenoma, and carcinoma individuals using HPLC.} Acetate (A),
butyrate (B), and propionate (C) concentrations in fecal samples of
individuals without colon tumors (Normal), adenomas, and carcinomas (C).
The black lines indicate the median SCFA concentration. Acetate (D),
butyrate (E), and propionate (F) concentrations in fecal samples before
and after treatment for adenoma (yellow) and carcinoma (red). The black
dots and lines represent the median change in SCFA concentration.
